### 2021-08-22 plos_latex_template.tex
Edited online rule

\section*{Rule 1: Embrace all dimensions of diversity}

@@

As a starting point, identify which groups are usually unsupported or discriminated against in the community or event of interest, and determine the contributing factors. Next, think about set measurable indicators of success when organizing a diverse conference. The numbers resulting from these indicators are not the primary goal. Instead, this vision should guide and help hold the organizing team accountable towards these diverse and inclusive goals.

@@

\section*{Rule 2: Have an inclusive and diverse organizing team}
A genuinely inclusive conference can only be organized by an inclusive and diverse organizing team. Build a team with people from different regions, genders, socioeconomic statuses, and other aspects of diversity. Particular attention should be paid to the usually underrepresented groups (see \textbf{Rule 1} discussing the dimensions of diversity lacking in your community and event). To ensure a deeper understanding of the challenges in different diverse groups, it is essential to create a representative working group that functions as a snapshot of the community at large. Even if creating and maintaining such an interdisciplinary team is challenging, the positive outcomes far outweigh any minor inconveniences, and the team will grow, learn, and embrace more inclusive practices. For instance, if the organizing team is global and remote, time zones can be hard to manage, with meetings scheduled at odd hours. The team may also have to review carefully and teach themselves the correct vocabulary for internal and external communication and identify the best ways to account for every culture and situation. 
An inclusive team will let everyone know if the organization is failing in any aspect of inclusiveness or accessibility, and help improve it \cite{hong_groups_2004}.

@@

\section*{Rule 3: Search proactively the best people for each task}

@@

\section*{Rule 4: Set registration rates commensurate with the registrant's cost of living}

@@

\section*{Rule 5: Abandon diversity scholarships}

@@

\section*{Rule 6: Make the conference accessible to all, from start to end}

@@

\section*{Rule 7: Take deliberate efforts to promote the conference among underrepresented groups}

@@

\section*{Rule 8: Have a strong online component of the conference}

In-person interaction is priceless; however, it is more expensive for some, even unattainable for others \cite{arend_disparity_2019, timperley_he_2020, niner_better_2021}. This inaccessibility is particularly true for global conferences that usually take place in high-income countries, making it financially demanding for international participants and often impossible to attend due to immigration requirements \cite{sarabipour_evaluating_2020, gewin_what_2019}. Online conferences are more inclusive and do not need a visa or a big budget.

\section*{Rule 9: Don't let language restrict high-quality participation}

@@

\section*{Rule 10: Have a code of conduct and a team to reinforce it}

>>>>

\section{Rule X: Define what diversity and inclusion mean for your conference}

@@

As a starting point, identify which groups are usually unsupported or discriminated against in your community or event, and determine the contributing factors. Next, think about set measurable indicators of success when organizing a diverse conference. The numbers resulting from these indicators are not the primary goal. Instead, this vision should guide and help hold the organizing team accountable towards these diverse and inclusive goals.

@@

\section{Rule X: Have a strong online component of the conference}

In-person interaction is priceless; however, it is more expensive for some, even unattainable for others. This inaccessibility is particularly true for global conferences that usually take place in high-income countries, making it financially demanding for international participants and often impossible to attend due to immigration requirements \cite{arend_disparity_2019, gewin_what_2019}. Online conferences are more inclusive: they do not need a visa or a big budget, and are more accessible to people who may be unable to travel because of health issues or family responsibilities. Furthermore, an online format is more environmentally friendly since it eliminates travel-related emissions \cite{sarabipour_evaluating_2020, niner_better_2021}; in a study case, conference attendance accounted for $35\%$ of a researchers footprint .

\section{Rule X: Have an inclusive and diverse organizing team}
A genuinely inclusive conference can only be organized by an inclusive and diverse organizing team. Build a team with people from different regions, genders, socioeconomic statuses, and other aspects of diversity. Particular attention should be paid to the usually underrepresented groups (see \textbf{Rule 1} discussing the dimensions of diversity lacking in your community and event). To ensure a deeper understanding of the challenges in different diverse groups, it is essential to create a representative working group that functions as a snapshot of the community at large. Even if creating and maintaining such an interdisciplinary team is challenging, the positive outcomes far outweigh any minor inconveniences, and the team will grow, learn, and embrace more inclusive practices. For instance, if the organizing team is global and remote, time zones can be hard to manage, with meetings scheduled at odd hours. The team may also have to review carefully and teach themselves the correct vocabulary for internal and external communication and identify the best ways to account for every culture and situation. 
An inclusive team will let everyone know if the organization is failing in any aspect of inclusiveness or accessibility, and help improve it \cite{hong_groups_2004}.

@@

\section{Rule X: Search proactively the best people for each task}

@@

\section{Rule X: Set registration rates commensurate with the registrant's cost of living}

@@

\section{Rule X: Abandon diversity scholarships}

@@

\section{Rule X: Make the conference accessible to all, from start to end}

@@

\section{Rule X: Take deliberate efforts to promote the conference among underrepresented groups}

@@

\section{Rule X: Don't let language restrict high-quality participation}

@@

\section{Rule X: Have a code of conduct and a team to reinforce it}
